From Education to Entrepreneurship

### 2014-12-06 index.Rmd
Created imputed dataframes
Added imputed dfs

>>>>

```{r echo = FALSE, cache= TRUE, include= FALSE, results= 'asis'}
RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)

# Library Zelig (can be buggy if loaded to early)
library(Zelig)
library("Amelia")

# Omit omitted data from simulation
CD_omit <- na.omit(CD)

# Run a least squares regression with Zelig
Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omit, model = "ls")

summary(Z1)

# Impute missing values for regression analysis (Amelia)
Cimputed <- Amelia::amelia(CD, m = 5, idvars = c("iso2c", "Country"), ts = "Year")

# Create CSV of imputed values
write.amelia(Cimputed, "Cimputed", separate = TRUE, format = "csv")

# Set working directory to local repository
setwd('~/Assign2Education/')

# Open csv
Cimputed <- read.table("Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)

# Regression equation with imputed values
Z2 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = Cimputed, model = "ls")
```
